New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

### Teachers' self-assessment of arousal during the teaching phase

>>>>

### Teachers' self-assessment of arousal during the teaching phase
Two 11-point rating scales were used to assess the subject's self-assessment of arousal during the Stimulated Recall Interview. The rating scales collected data of the teacher's subjective perception of disruptiveness of a lesson event and their subjective perception of confidence in dealing with the event during the lesson.

For this purpose, the recording was stopped shortly before the respective disruption and first a stimulus was given to the following event, as well as the teacher was asked to briefly comment on the disturbance itself. The subjective perception of the disruptiveness of an event was asked following the teacher's elaboration on the disturbance in question as follows: "On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive" (see appendix).

The subjective confidence with regard to the respective classroom disruption was collected and measured in the same way as the subjective perception of disruptiveness. The collection of the data took place chronologically after the statements about the disruption perception. After the description and justification of the reaction, the feeling of safety in dealing with the classroom disturbance was asked as follows: "Please rate your confidence in dealing with the event on a scale of 0-10: How confident did you feel in dealing with this event? 0 is not confident at all and 10 is extremely confident" (see Appendix).

The response format was deliberately chosen to be closed and multilevel, since numerical values are thus assigned to the subjects' emotional world, and this can thus be made measurable and comparable (cf. Eid et al., 2013; Botz & Döring, 2016). The levels of the rating scale prepared for this purpose are unambiguous, and the distances between them were equal. The feature expression was estimated and verbally communicated by the subjects immediately after seeing the recording of the respective disturbance.
